%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------


% Define custom icon styles
\newcommand{\iconcolor}{blue} % Change the color here
\newcommand{\iconsize}{1.2em} % Change the size here
\begin{center}
    \textbf{\Huge \scshape Md Saiful} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.9pt} \href{tel:8801682523401}{+880 168 252 3401}
    $|$
    \faAt \hspace{.3pt} \href{mailto:saifulislamsarfaraz@gmail.com}{saifulislamsarfaraz@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.3pt} \href{https://www.linkedin.com/in/md-saiful-283000181/}{LinkedIn}
    $|$
    \faGithub \hspace{.3pt} \href{https://github.com/saifulislamsarfaraz}{GitHub}
    $|$
    \faGlobe \hspace{.3pt} \href{https://saifulislamsarfaraz.github.io}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://goo.gl/maps/HLA1nAP5VZEeo3DV8}{Dhaka, Bangladesh}
\end{center}


%----------- Summary -----------

\section{Summary}
  \vspace{4pt}
  \resumeSubHeadingListStart
 {A Computer Science and Engineering graduate from East West University who maintained 100\% scholarship and made the dean’s list for nine consecutive semesters, and possesses a strong interest in researching data science and machine learning in the hopes of making a substantial impact on the field.}
  \resumeSubHeadingListEnd


%----------- Summary -----------

\section{Research Interests}
  \vspace{4pt}
  \resumeSubHeadingListStart
 {Data Science, Big Data Analytics, Machine Learning, Natural Language Processing, Image Processing, Bioinformatics, Blockchain, Software Engineering}
  \resumeSubHeadingListEnd



%----------- EDUCATION -----------

\section{Education}
  \vspace{4pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {East West University
      % \normalfont{(Admission rate: 0.09\%)}
      }{Dhaka, Bangladesh}
      {B.Sc. in Computer Science and Engineering;   \textbf{GPA: 3.65/4.00}}{April 2019 \textbf{--} Aug 2023}
    \textbf{Thesis:} {MedicalBERT: A Medical Chatbot Built Using, BioBERT and GPT-2}

        % \resumeItemListStart
            % \resumeItem{\textbf{Relevant coursework:} Calculus I-II, Matrix Theory, Differential Equations, Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering}
        % \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
        
    \resumeSubheading
      {East West University}{Aftabnagar, Dhaka, Bangladesh }
      {Graduate Teaching Assistant}{Jul 2023 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{\textbf{Courses Taught:} Structured Programming (Programming language: C), Cyber Security, Image Processing.}
        \resumeItemListEnd
    \resumeSubheading
      {Techfinity}{North Baridhara, Merul Badda, Dhaka-1212, Bangladesh (On-site)}
      {Ass. Engineer and Developer}{February 2022 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Developed effective and affordable web design \& web development services with expert customer support.}
            \resumeItem{Reviewed, validated, and scored the AI assistants for Attendance Devices.}
            \resumeItem{Scheduling maintenance IT.}
        \resumeItemListEnd
        
    \resumeSubheading
      {East West University}{Aftabnagar, Dhaka, Bangladesh }
      {Undergraduate Teaching Assistant}{Jan 2022 \textbf{--} Jun 2022}
        \resumeItemListStart
            \resumeItem{\textbf{Courses Taught:} Structured Programming (Programming language: C), Image Processing.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Klatch Technologies}{Assam, India (Remote)}
      {AI Research and Development Intern}{Aug 2022 \textbf{--} Oct 2022}
        \resumeItemListStart
            \resumeItem{Implemented common NLP tasks using transformers such as named-entity recognition (NER), part-of-speech (POS) tagging, sentiment analysis, text classification, and extractive/generative question answering.}
            \resumeItem{Intent-based Query Model for Question Answering}
            \resumeItem{Worked on a custom Medical domain question-answering system by fine-tuning a BERT base model transformer. Evaluated the exact match and F1 scores using different Medical data sets and compared the evaluation results.}
        \resumeItemListEnd
    \resumeSubheading
      {UDVASH}{Motijheel Dhaka, Bangladesh (Part-time)}
      {Teacher}{Jan 2020 \textbf{--} Aug 2021}
        \resumeItemListStart

            \resumeItem{Work with students, and indoctrinate them about problems they are having with the course material.}
            \resumeItem{Holding 21 hours per week's office hours.}
            \resumeItem{Lead discussion sessions with students.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{4pt}
  {\textbf{Manuscripts Under Review}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{1. }{ MRI-Based Brain Tumor Classification Using Various Deep Learning Convolutional Networks and CNN, \textbf{Md. Saiful}, Sakib Haidar, S M Arafat Rahman,Nahid Reza, Ahmed Wasif Reza and Mohammad Samsul Arafin.6th International Conference on Intelligent Computing and Optimization April 27-28, 2023 | G Hua Hin Resort \& Mall, Hua Hin, Thailand.} \\ \vspace{3pt}
    
        \textbf{2. } {Brain MRI Classification for Alzheimer's Disease Based on Convolutional Network, \textbf{Md. Saiful}, Arpita Saha, Faria Tabassum mim, Nafisa Tasnim, Ahmed Wasif Reza and Mohammad Samsul Arafin. 6th International Conference on Intelligent Computing and Optimization April 27-28, 2023 | G Hua Hin Resort \& Mall, Hua Hin, Thailand.} \\ \vspace{3pt}
        
        \textbf{3. } {Green Banking Through Blockchain-Based Application for Secure Transactions, \textbf{Md. Saiful}, Nahid Reza, Maisha Mahajabin, Syada Tasfia Rahman,Farhana Alam, Ahmed Wasif Reza and Mohammad Samsul Arafin. 6th International Conference on Intelligent Computing and Optimization April 27-28, 2023 | G Hua Hin Resort \& Mall, Hua Hin, Thailand.} \\ \vspace{3pt}

        \textbf{4. } {Solving Hamiltonian Path Problem Using DNA Computing, Mahamudul Hasan and \textbf{Md. Saiful}, Taskeed Jabid, Maheen Islam, Md Ali, Riaz Murshed Rifat, Rubaya Bari, Nusrat Jahan and Tanni Rani Pal. International Conference on Green Energy, Computing and Intelligent Technology (GEn-CITy 2023) 10-12 July 2023|University of Southampton Malaysia congratulates} \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd





%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{100\% Merit Scholarship \& Dean List}{For achieving a CGPA of 3.90 or above (3.97) out of 4.00 for three consecutive semesters (Summer 2022 -Summer 2023.} \\ \vspace{3pt}
    
        \textbf{50\% Merit Scholarship \& Dean List}{ For achieving a CGPA of 3.90 or above (3.97) out of 4.00 for three consecutive semesters (Summer 2021 -Summer 2022 } \\ \vspace{3pt}

        \textbf{Best Volunteer Award:}{ Awarded to best Volunteer perform IEEE Computer Society BDC Summer Symposium 2023.} \\ \vspace{3pt}
        \textbf{Awarded Best cadet:}{ Awarded to the cadet who has outstanding performance among 200 cadets.} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Trash Collector Smart Recycling Technology using Deep Learning Approach } $|$ \emph{\href{https://github.com/saifulislamsarfaraz/brain-tumor-detection}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{In this project, Real-time object detection and collect trash mechanism using deep learning. Here I used to train the Resnet152 model for train and accuracy to get 94\%}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Credit Card Fraudulent Detection} $|$ \emph{\href{https://github.com/saifulislamsarfaraz/Credit-Card-Fraud-Detection-with-Matchine-learning}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Credit Card Fraud Detection using Machine Learning which is implemented with Decision Tree, Logistic Regression, SMOTE, XGboost Models get the Logistic regression model with SMOTE is the best model for its simplicity and less resource requirement.}
          \resumeItemListEnd
                \resumeProjectHeading
        {\textbf{MRI Image Segmentation for Detecting Brain Tumor} $|$ \emph{\href{https://github.com/saifulislamsarfaraz/brain-tumor-detection}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{For Detecting Image I have done segmentation Making Mask Preparing data Building U-net CNN model Training the model Evaluation Model on some training data Evaluation model on the test data}
            \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Hotel Management System Covid-19} $|$ \emph{\href{https://github.com/saifulislamsarfaraz/The-hotel-management-system-Covid-19}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Real-time Employee management system object and Face Recognition using RCNN, Redis Docker, Django}
            \resumeItem{Manage category of room, Health care, and payment. Based on the customer's situation suggest a hospital}
          \resumeItemListEnd
      
      % \resumeProjectHeading
        % {\textbf{Rocket Flight Simulator} $|$ \emph{\href{https://github.com/arasgungore/rocket-flight-simulator}{\color{blue}GitHub}}}{}
          % \resumeItemListStart
            % \resumeItem{A Simulink project which can accurately simulate the motion of a flying rocket in one-dimensional space.}
            % \resumeItem{The project implements the forces acting on a rocket which are drag, weight, and thrust as subsystems that take time-variant parameters into consideration such as distance from the center of Earth, mass and velocity of the rocket, and air density at different layers of Earth's atmosphere.}
          % \resumeItemListEnd
      
      % \resumeProjectHeading
        % {\textbf{Netlist Solver} $|$ \emph{\href{https://github.com/arasgungore/netlist-solver}{\color{blue}GitHub}}}{}
          % \resumeItemListStart
            % \resumeItem{A MATLAB project that uses modified nodal analysis (MNA) algorithm to calculate the node voltages of any analog circuit without dependent sources given in netlist format.}
            % \resumeItem{Added a module that sweeps the resistance of a load resistor, plots power dissipation as a function of load resistance, and finds the resistance value corresponding to maximum power.}
          % \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{SSL Certificate Generation and Authentication} $|$ \emph{\href{https://github.com/saifulislamsarfaraz/Computer-and-Cybersecurity}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Cyber Security Course Project SSL certificate generation using OpenSSL. Intuition Detection, Firebase.}
            \resumeItemListEnd
      
    \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ C, C++, Java, Python, JavaScript, R, MATLAB, SQL, MySQL} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Git, Docker, OpenCV, Arduino, Redis,} \\ \vspace{3pt}
        
        \textbf{Languages:}{ Bangla (Native), English (Professional)}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd


\section{Competitive Programming}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Problem-Solving: } {Solved numerous algorithmic problems and participated in online programming contests in various online judges including Codeforces, Codechef, UVa, and Atcoder. also A am a } \textbf{Contest Trainer:} { I take classes on competitive programming at Binary Coder Bd.} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd

%----------- RELEVANT COURSEWORK -----------

%\section{Relevant Coursework}
%  \vspace{2pt}
%  \resumeSubHeadingListStart
%    \small{\item{
%        \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}
        
%        \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
%    }}
%  \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
